A Generic and Efficient E-field Parallel Imaging Correlator for Next-Generation Radio Telescopes

### 2016-12-18 imaging_demo/ms.tex
Start addressing second round of referee report
From 25eeda9 (mnras):
====================

(*) Update figures to have uniform properties as per second round of
referee report
Give heterogeneous array imaging analysis context
From 1c821b1 (mnras):
====================

In epic.bib,

(*) Add Iguchi et al. (2009) reference

In ms.tex,

(*) Add a couple of paragraphs in section 5 to set up the context of
heterogeneous array imaging analysis

\begin{figure}
  \includegraphics[width=\columnwidth]{figure6}
  \caption{Synthesized beams weighted by antenna power pattern sliced at $m=0$ obtained with MOFF algorithm using EPIC (solid black line) and visibility-based imaging (dashed gray line). The two appear almost identical. The inset provides a magnified view of differences in the synthesized beam slices between the two techniques at levels $\lesssim 0.5$\% relative to the peak. These are attributed to differences that arise in gridding and depends on the coarseness of the grid.}
  \label{fig:MOFF-FX-psf-diff}
\end{figure}

@@

\begin{figure}
  \includegraphics[width=\columnwidth]{figure7}
  % \includegraphics[width=\columnwidth]{MOFF_FX_comparison_uvwts_test_aperture_zero_spacing_removed}
  % \includegraphics[width=\columnwidth]{MOFF_FX_comparison_uvwts_test_aperture_zero_spacing_removed.eps}
  \caption{{\it Left}: Differences (in \%) in cross-correlated weights in the $uv$ plane relative to the peak. The biggest difference ($\sim 20$\%) is found around the zero-spacing corresponding to auto-correlations of antenna weights due to gridding differences augmented by the relatively high number density of antenna auto-correlation footprints in that region. In most of the other regions, differences of the order of less than a few percent are seen. {\it Right}: Histogram (expressed as percentage) of the relative differences (in \%) between antenna cross-correlation weights shown on the left binned in intervals of 0.5\%. Over 70\% of the $uv$-cells do not differ by more than 0.5\% and over 90\% of $uv$-cells only differ by $<5$\% for the gridding coarseness used.} 
  \label{fig:MOFF-FX-uvwts-diff}
\end{figure}

@@

@@

This demonstrates that images from EPIC can robustly image data from heterogeneous arrays while being mathematically optimal. Besides being sub-optimal, erroneous assumptions about the homogeneity of an array can lead to significant and systematic mis-estimates (in this case, an underestimate) of the sky model.

@@

\begin{figure}
  \includegraphics[width=\columnwidth]{figure12}
  % \includegraphics[width=\columnwidth]{MOFF_FX_crossover_baseline_n-antennas_rho_fov_gridding_legended}
  % \includegraphics[width=\columnwidth]{MOFF_FX_crossover_baseline_n-antennas_rho_fov_gridding_legended.eps}
  \caption{Current and planned instruments in parameter space of baseline length and number of antennas with MOFF and FX. Lines of different colors denote different classes of antenna sizes (cyan - 1~m$^2$, blue - 7~m$^2$, purple - 16~m$^2$, green - 28~m$^2$, orange - 150~m$^2$, red - 740~m$^2$, gray - 5900~m$^2$). Lines of each color denote the boundary to the left of which MOFF algorithm is favoured for the corresponding antenna size. These lines shift rightward with increasing antenna size. The different antennas are color coded by roughly the class of antenna size they fall into. Thus symbols of one color falling to the left of a line of the same color indicate MOFF imaging is advantageous for those telescopes and vice versa. For example, MOFF imaging is favoured in HERA-331 and HERA-6769 because they lie to the left of the orange line but not so in cases of HERA-19 and HERA-37.}
  \label{fig:parameter-space-bll-nant-instruments}
\end{figure}

>>>>

\begin{figure}
  \includegraphics[width=\columnwidth]{figure6}
  % \includegraphics[width=\columnwidth]{MOFF_FX_synthesized_beam_slices}
  \caption{Synthesized beams weighted by antenna power pattern sliced at $m=0$ obtained with MOFF algorithm using EPIC (solid black line) and visibility-based imaging (dashed gray line). The two appear almost identical. The inset provides a magnified view of differences in the synthesized beam slices between the two techniques at levels $\lesssim 0.5$\% relative to the peak. These are attributed to differences that arise in gridding and depends on the coarseness of the grid.}
  \label{fig:MOFF-FX-psf-diff}
\end{figure}

@@

\begin{figure}
  \includegraphics[width=\columnwidth]{figure7}
  % \includegraphics[width=\columnwidth]{MOFF_FX_fracdiff_uvwts_test_aperture_zero_spacing_removed}
  % \includegraphics[width=\columnwidth]{MOFF_FX_fracdiff_uvwts_test_aperture_zero_spacing_removed.eps}
  \caption{{\it Left}: Differences (in \%) in cross-correlated weights in the $uv$ plane relative to the peak. The biggest difference ($\sim 20$\%) is found around the zero-spacing corresponding to auto-correlations of antenna weights due to gridding differences augmented by the relatively high number density of antenna auto-correlation footprints in that region. In most of the other regions, differences of the order of less than a few percent are seen. {\it Right}: Histogram (expressed as percentage) of the relative differences (in \%) between antenna cross-correlation weights shown on the left binned in intervals of 0.5\%. Over 70\% of the $uv$-cells do not differ by more than 0.5\% and over 90\% of $uv$-cells only differ by $<5$\% for the gridding coarseness used.} 
  \label{fig:MOFF-FX-uvwts-diff}
\end{figure}

@@

{\bf Heterogeneity in antenna arrays occurs primarily in two scenarios. The first is when the array is intended to be identical but differences in aperture and electrical properties arise due to deviations during the manufacturing process or from random deviant behaviour such as in dipoles of a phased array. The second scenario is when the array is designed to be heterogeneous to gain specific advantages such as sampling a wider range of spatial frequencies and decoupling the sky brightness distribution from the antenna power pattern. This has motivated a number of heterogeneous arrays such as the Combined Array for Research in Millimeter-wave Astronomy (CARMA; \citealt{woo04,wri10}), the Atacama Large Millimeter/submillimeter Array (ALMA; \citealt{igu09}), and the Very Long Baseline Array (VLBA). In practice, almost all arrays are heterogeneous albeit by varying degrees. The following analysis applies to both of the aforementioned scenarios although for purposes of clear demonstration, we will choose an example that is closer to the second scenario.}

@@

This demonstrates that images from EPIC can robustly image data from heterogeneous arrays while being mathematically optimal. Besides being sub-optimal, erroneous assumptions about the homogeneity of an array can lead to significant and systematic mis-estimates ({\bf an underestimate in the above example}) of the sky model.

{\bf In the above example, we chose a scenario wherein the antennas in the array have large differences between them to clearly demonstrate the functionality in EPIC to image data from heterogeneous arrays. The analysis, however, is applicable to any heterogeneous array. In cases where the differences are smaller, the fidelity with which the sky model is recovered will still be degraded, although to a correspondingly smaller extent. To robustly quantify this degradation as a function of deviation from homogeneity will require image deconvolution and will be investigated in the future as it is currently beyond the scope of this paper.}

@@

\begin{figure}
  \includegraphics[width=\columnwidth]{figure12}
  % \includegraphics[width=\columnwidth]{MOFF_FX_crossover_baseline_n-antennas_rho_fov_gridding_legended_v2}
  % \includegraphics[width=\columnwidth]{MOFF_FX_crossover_baseline_n-antennas_rho_fov_gridding_legended_v2.eps}
  \caption{Current and planned instruments in parameter space of baseline length and number of antennas with MOFF and FX. Lines of different colors denote different classes of antenna sizes (cyan - 1~m$^2$, blue - 7~m$^2$, purple - 16~m$^2$, green - 28~m$^2$, orange - 150~m$^2$, red - 740~m$^2$, gray - 5900~m$^2$). Lines of each color denote the boundary to the left of which MOFF algorithm is favoured for the corresponding antenna size. These lines shift rightward with increasing antenna size. The different antennas are color coded by roughly the class of antenna size they fall into. Thus symbols of one color falling to the left of a line of the same color indicate MOFF imaging is advantageous for those telescopes and vice versa. For example, MOFF imaging is favoured in HERA-331 and HERA-6769 because they lie to the left of the orange line but not so in cases of HERA-19 and HERA-37.}
  \label{fig:parameter-space-bll-nant-instruments}
\end{figure}
